HPC--101\\Onboarding

### 2016-01-22 hpc_101/paper.tex
missing word in faq

\item Help I have been trying to compile an application without success, can the {\citeam} help?
  \begin{itemize}\tiny
  \item \textbf{Answer:} We are willing to help, just send us an email at \textit{uh-hpc-help@lists.hawaii.edu} with a description of what you have attempted as well a link to the software you are trying to compile, and/or where it is located on the cluster.
  \end{itemize}

>>>>

\item Help I have been trying to compile an application without success, can the {\citeam} help?
  \begin{itemize}\tiny
  \item \textbf{Answer:} We are willing to help, just send us an email at \textit{uh-hpc-help@lists.hawaii.edu} with a description of what you have attempted as well as a link to the software you are trying to compile, and/or where it is located on the cluster.
  \end{itemize}
